\chapter{Technology}\label{ch:technology}
\epigraph{\textit{\Large “I think, therefore I am”}}{\textit{ \large René Descartes,\\ French philosopher and scientist}}
\begin{itemize}
	\item\textbf{Adversarial Training:} Two models undergoing training simultaneously by competing against each other. The output of each model acts as an adversary for the other to improve upon.
	\item\textbf{Generative Model:} Any model capable of generating completely new realistic data of a class.
	\item\textbf{Discriminitive Model:} Here, as a Discriminator, a model which is capable of distinguishing between actual ground truth from the true distribution and generated information from a model.
	\item\textbf{Gradient Descent:} A method of optimising an objective function using a first-order iterative appraoch to find a local minimum.
	\item\textbf{Gaussian Model:} A model that fits the data in the shape of a Gaussian function, identified by a characteristic "bell curve". CapsNet uses this to find agreeing probabilty outputs of the "capsules".
	\item\textbf{TensorFlow:} An open source software library for numerical computation using data flow graphs. It was originally developed by the Google Brain Team within Google's Machine Intelligence research organization for machine learning and deep neural networks research.

\end{itemize}

\textbf{\Large Other essentials:}

\begin{itemize}
	\item\textbf{CPU:} 3GHz quad core, x86-64 architecture (or)
	\item\textbf{GPU:} NVIDIA or any other TensorFlow supported GPU, CUDA or cuDNN
	\item\textbf{Python:} 2.7 or 3.4 and above
\end{itemize}
