\chapter*{Acknowledgments}
\noindent This project would not have been possible without the contributions of many people.\par\bigskip
We are pleased to express our sincere thanks to the administration of the \textbf{Sir M. Visvesvaraya Institute of Technology}, Bangalore, which has given us the opportunity and the resources to carry out our projects in their facilities.\par\bigskip
We would also like to convey our sincere thanks \textbf{Dr. V. R. Manjunath}, principal, Sir MVIT for providing us with the infrastructure and facilities needed to develop our project.\par\bigskip
We would like to thank the \textbf{Prof Dilip K. Sen}, Head of the department, CSE, Sir MVIT for providing an intellectual environment where we could devote a tremendous amount of time to work on this project.\par\bigskip
We wish to express our heartfelt gratitude to our guide, \textbf{Smt. Sushila Shidnal}, for her invaluable guidance, encouragement, support and advice.\par\bigskip
We thank \textbf{Google} for \textbf{Google colaboratory} where we ran most of our Deep Learning model training.\par\bigskip
Our immense gratitude for the members of faculty of \textbf{Department of Computer Science and Engineering}, Sir MVIT for support and co-operation. Lastly we thank all our friend for their help and suggestion without which this project would not have been possible.\par\bigskip
\vspace{50px}
\noindent\hfill\begin{tabular}{ l r }
        \textsc{-  \textbf{Abhijith C.}}       &  \textbf{1MV14CS004} \\
        \textsc{-  \textbf{Raghava G. Dhanya}} &  \textbf{1MV14CS077} \\
        \textsc{-  \textbf{Shashank S.}}       &  \textbf{1MV14CS131}
\end{tabular}