\chapter{System Requirements}\label{ch:system_requirements}
\epigraph{\textit{\normalsize “Any A.I. smart enough to pass a Turing test is smart enough to know to fail it.”}}{\textit{ \normalsize Ian McDonald,\\ River of Gods}}

\section{Functional Requirements} % (fold)
\label{sec:functional_requirements}
The system must, at the minimum, fulfill certain basic requirements.
\begin{enumerate}
    \item Take a latent space vector or noise as input.
    \item Learn joint probability distribution of training images.
    \item Generate a realistic image of the training distribution that doesn't belong to training set.
    \item Use a binary Capsule network classifier to differentiate real and fake image.
\end{enumerate}
% section functional_requirements (end)
\section{Non Functional Requirements} % (fold)
\label{sec:non_functional_requirements}
The system should have following non functional requirements. These specify the qualities of the system.
\begin{enumerate}
    \item Efficient, Fast forward- and backward- propagation.
    \item Curb data usage while maintaining high quality results.    
\end{enumerate}
% section non_functional_requirements (end)

\section{Development Requirement} % (fold)
\label{sec:development_requirement}
\noindent
System requirements for training and demonstrating of the models
\subsection{Training System Requirements} % (fold)
\label{sub:training_system_requirements}
For training the model,
\begin{enumerate}
    \item python 3.4 or above
    \item Tensorflow 1.7 or above
    \item Keras  2.1.6 or above
    \item Numpy, Scipy, Matplotlib
    \item OpenCV 2
    \item CPU 1.6 GHz or above
    \item Nvdia GPU with CUDA compatibility 3.5 or above
    \item RAM 8GB or above
    \item Disk storage 20GB or above
\end{enumerate}
% subsection training_system_requirements (end)

\subsection{Demonstration System Requirements} % (fold)
\label{sub:demonstration_system_requirements}
For evaluating the model or just forward-propagation,
\begin{enumerate}
    \item python 3.4 or above
    \item Flask
    \item Browser - Google Chrome
    \item Tensorflow 1.7 or above
    \item Keras  2.1.6 or above
    \item Numpy, Scipy, Matplotlib
    \item OpenCV 2
    \item CPU 1 GHz or above
    \item RAM 4GB or above
    \item Disk storage 20GB or above
\end{enumerate}
% section development_requirement (end)